Impact of Pandemic Policies on Rural Indian Women's Mental Health and Economic Stability

### 2024-04-19 outputs/paper.qmd
figure legend

# Model
Different models were used to evaluate diffrent factors to Indian women's well-being during the pandemic.

I employ a regression model to assess the impact of district-level containment measures on individual outcomes, considering age, state, and district variables. Myoutcome of interest reflects various personal experiences, with containment representing the intensity of policy measures in one's district.

The model accounts for age and state as non-varying influences, along with controls for local COVID-19 severity and pre-pandemic socioeconomic factors to mitigate potential confounding effects. I ensure a consistent sample across studies by including only individuals with complete control data.

@@

### Model Variables:

- `$y_{iasd}$`: The outcome variable for an individual, such as mental health or economic status.
- `$\beta \text{containment}_d$`: Coefficient for containment policies in the individual's district, measuring the impact of these policies on the outcome.
- `$\alpha_a$`: Age fixed effects to control for age-related variations in the outcome.
- `$\delta_s$`: State fixed effects to account for differences attributable to the state of residence.
- `$\Gamma X_i$`: Effects of control variables, including indicators for the district being in a red or orange zone during specific lockdown periods.
- `$\epsilon_{iasd}$`: Error term capturing unobserved influences on the outcome.

@@

```{r}
#| label: fig-3
#| fig-cap: "Relationship between Containment and Female Well-being or Socioeconomic and Nutritional Outcomes."
#| echo: false
#| warning: false
#| message: false
#| fig-subcap: ["Effect Sizes of Predictors in Mental Health Models", "Effect Sizes of Predictors in Economic and Nutritional Impact Models"]

@@

# Plotting functions
plot_coefficients_logistic <- function(results) {
  ggplot(results, aes(x = term, y = estimate, color = model)) +
    geom_point(position = position_dodge(width = 0.5)) +
    geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.2, position = position_dodge(width = 0.5)) +
    coord_flip() +
    labs(x = "Predictors", y = "Estimated Coefficients") +
    theme_minimal() +
    theme(legend.title = element_blank(),
          legend.position = "bottom")
}

plot_coefficients_felm <- function(results) {
  ggplot(results, aes(x = term, y = estimate, color = model)) +
    geom_point(position = position_dodge(width = 0.5)) +
    geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.2, position = position_dodge(width = 0.5)) +
    coord_flip() +
    labs(x = "Predictors", y = "Estimated Coefficients") +
    theme_minimal() +
    theme(legend.title = element_blank(),
          legend.position = "bottom")
}

@@

results_felm <- summarize_models(results_vars_interest)
plot_felm <- plot_coefficients_felm(results_felm)
print(plot_felm)
```
I conducted an analysis that focused on key predictor variables, such as the number of COVID-19 cases and deaths per 100,000, the proportion of districts in designated COVID zones, and the different containment zone statuses like Red and Orange Zones. I aimed to find connections between these predictors and the mental health outcomes among women during the pandemic, focusing on changes in depression, tiredness, and safety concerns.

>>>>

# Model
Different models were used to evaluate diffrent factors to Indian women's well-being during the pandemic.I employ a regression model to assess the impact of district-level containment measures on individual outcomes, considering age, state, and district variables. Myoutcome of interest reflects various personal experiences, with containment representing the intensity of policy measures in one's district. The model accounts for age and state as non-varying influences, along with controls for local COVID-19 severity and pre-pandemic socioeconomic factors to mitigate potential confounding effects. I ensure a consistent sample across studies by including only individuals with complete control data.

@@

## Model Variables:

- $y_{iasd}$: The outcome variable for an individual, such as mental health or economic status.
- $\beta \text{containment}_d$: Coefficient for containment policies in the individual's district, measuring the impact of these policies on the outcome.
- $\alpha_a$: Age fixed effects to control for age-related variations in the outcome.
- $\delta_s$: State fixed effects to account for differences attributable to the state of residence.
- $\Gamma X_i$: Effects of control variables, including indicators for the district being in a red or orange zone during specific lockdown periods.
- $\epsilon_{iasd}$: Error term capturing unobserved influences on the outcome.

@@

```{r}
#| label: fig-3
#| fig-cap: "Relationship between Containment and Female Well-being or Socioeconomic and Nutritional Outcomes."
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8 
#| fig-height: 4 
#| fig-subcap: ["Effect Sizes of Predictors in Mental Health Models", "Effect Sizes of Predictors in Economic and Nutritional Impact Models"]

@@

# Plotting functions
plot_coefficients_logistic <- function(results) {
  ggplot(results, aes(x = term, y = estimate, color = model)) +
    geom_point(position = position_dodge(width = 0.5)) +
    geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.2, position = position_dodge(width = 0.5)) +
    coord_flip() +
    labs(x = "Predictors", y = "Estimated Coefficients") +
    theme_minimal() +
    theme(legend.title = element_blank(),
          legend.position = "right")
}

plot_coefficients_felm <- function(results) {
  ggplot(results, aes(x = term, y = estimate, color = model)) +
    geom_point(position = position_dodge(width = 0.5)) +
    geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.2, position = position_dodge(width = 0.5)) +
    coord_flip() +
    labs(x = "Predictors", y = "Estimated Coefficients") +
    theme_minimal() +
    theme(legend.title = element_blank(),
          legend.position = "right")
}

@@

results_felm <- summarize_models(results_vars_interest)
plot_felm <- plot_coefficients_felm(results_felm)
print(plot_felm)
```

I conducted an analysis that focused on key predictor variables, such as the number of COVID-19 cases and deaths per 100,000, the proportion of districts in designated COVID zones, and the different containment zone statuses like Red and Orange Zones. I aimed to find connections between these predictors and the mental health outcomes among women during the pandemic, focusing on changes in depression, tiredness, and safety concerns.
